Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-23 paper/ms.tex
Summary images
Switched to AASTeX

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers
\usepackage[left=2cm,top=3cm,right=2cm]{geometry}

\renewcommand{\topfraction}{0.85} \renewcommand{\textfraction}{0.1} 
\parindent=0cm
\newcommand{\sparse}{\texttt{Sparse}}
\newcommand{\cluster}{\texttt{Cluster}}
\newcommand{\crowded}{\texttt{Crowded}}

\title{Probabilistic Catalogs for Crowded Stellar Fields}
\author{Brendon J. Brewer$^{1,*}$, David W. Hogg$^{2}$,
and Daniel Foreman-Mackey$^{2}$ \\
\\
\small
$^1$ Department of Statistics, The University of Auckland,\\
\small
Private Bag 92019, Auckland 1142, New Zealand \\
\small
$^2$ Center for Cosmology and Particle Physics, Department of Physics,
New York University,\\
\small
4 Washington Place, New York, NY, 10003, USA\\
\small
$^*$\texttt{bj.brewer@auckland.ac.nz}
}

\begin{document}
\maketitle

\abstract{We introduce a probabilistic (Bayesian) method for producing catalogs
from images of crowded stellar fields. The method is capable of handling the
challenges introduced by overlapping sources and is able to determine the luminosity
function of the stars even when the precise luminosity of each star is uncertain.
This is in contrast with standard techniques which make a single catalog,
potentially underestimating the uncertainties in any study of the stellar
population. The method is implemented using advanced Markov Chain Monte Carlo
(MCMC) techniques including Reversible Jump and Nested Sampling.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainty.}

@@

>>>>

\documentclass[manuscript]{aastex}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{bj.brewer@auckland.ac.nz}

\shorttitle{Probabilistic Stellar Catalogs}
\shortauthors{Brewer et al.}

\begin{document}

\title{Probabilistic Catalogs for Crowded Stellar Fields}

\author{Brendon J. Brewer}
\affil{Department of Statistics, The University of Auckland,
Private Bag 92019, Auckland 1142, New Zealand}

\author{David W. Hogg}
\affil{Center for Cosmology and Particle Physics, Department of Physics,
New York University, Washington Place, New York, NY, 10003, USA}

\and

\author{Daniel Foreman-Mackey}
\affil{Center for Cosmology and Particle Physics, Department of Physics,
New York University, Washington Place, New York, NY, 10003, USA}

\begin{abstract}We introduce a probabilistic (Bayesian) method for producing catalogs
from images of crowded stellar fields. The method is capable of handling the
challenges introduced by overlapping sources and is able to determine the luminosity
function of the stars even when the precise luminosity of each star is uncertain.
This is in contrast with standard techniques which make a single catalog,
potentially underestimating the uncertainties in any study of the stellar
population. The method is implemented using advanced Markov Chain Monte Carlo
(MCMC) techniques including Reversible Jump and Nested Sampling.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainty.
\end{abstract}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/summaries.eps}
\end{center}
\caption{Summary images for test case 2.\label{fig:summaries}}
\end{figure}
